### 2021-08-31 presentation/presentation.tex
update qr code
change color theme

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

@@

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\title[Detect. and Mitigation of Corrupted Info. in DMPC Based on Resource Allocation] % (optional, use only with long paper titles)
{Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation}

@@

\author[Nogueira, Bourdais, Guéguen] % (optional, use only with lots of authors)
{R. A. Nogueira \and R. Bourdais \and H. Guéguen}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[IETR --- CentraleSupélec] % (optional, but mostly needed)
{
  % \inst{1}%
  AUT Department\\
  IETR --- CentraleSupélec
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

@@

\pgfdeclareimage[height=0.5cm]{university-logo}{../img/logos/supelec.jpeg}
\logo{\pgfuseimage{university-logo}}

@@

    % The following outlook is optional.
    \vskip0pt plus.5fill
    \begin{itemize}
      \item
            Outlook
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
              \item
                    Non-linear attack model
            \end{itemize}
      \item Repository

                    \begin{minipage}{.6\textwidth}
                      \url{https://github.com/Accacio/SysTol-21}
                    \end{minipage}
                    \begin{minipage}{.2\textwidth}
                      \includegraphics[width=2cm]{../article/img/qrRepo.png}
                    \end{minipage}
    \end{itemize}
  \end{minipage}
\end{frame}

>>>>

\mode<presentation>
{
  \usetheme{Luebeck}
  % \usetheme{Madrid}
  % \usetheme{Warsaw}
  % \usetheme{Copenhagen}
  % \usecolortheme{beaver}
  % \usecolortheme{rose}
  % or ...
  % \usecolortheme{beaver}
  \useoutertheme{split}
  \useinnertheme{circles}

  \setbeamercolor{palette primary}{bg=red!50!black!80}
  \setbeamercolor{palette secondary}{bg=red!50!black!70}
  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
  \setbeamercolor{palette quaternary}{bg=gray!90!black!100}

  \setbeamercolor{item}{fg=red!50!black!80}
  \setbeamercolor{section in toc}{fg=red!50!black!80}

  % \setbeamercolor{author in head/foot}{bg=grey!60}
  \setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
\makeatletter
\setbeamertemplate{page number in head/foot}[appendixframenumber]
\setbeamertemplate{headline}
{%
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \centering
    \usebeamerfont{author in head/foot}\insertsection{}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
    \centering
    \insertsubsection{}
  \end{beamercolorbox}%
  }%
  \vskip0pt%
}
\setbeamertemplate{footline}
{%
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}%
    \centering
    \usebeamerfont{date in head/foot}\usebeamercolor[fg]{page number in head/foot}\usebeamerfont{page number in head/foot}\usebeamertemplate{page number in head/foot}
    % \hspace*{2ex}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \centering
    \usebeamerfont{author in head/foot}\insertshortauthor{}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.65\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
    \centering
    \insertshorttitle{}
  \end{beamercolorbox}%
  }%
  \vskip0pt%
}
\makeatother

  % or whatever (possibly just delete it)
}

@@

% \usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\title[Detection and Mitigation of Corrupted Information in DMPC Based on Resource Allocation] % (optional, use only with long paper titles)
{Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation}

@@

\author[Nogueira, Bourdais, Guéguen] % (optional, use only with lots of authors)
{R. A. Nogueira \and R. Bourdais \and H. Guéguen\\
\texttt{\{rafael-accacio.nogueira,romain.bourdais,herve.gueguen\}\ at \ centralesupelec.fr}}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[IETR --- CentraleSupélec] % (optional, but mostly needed)
{
  % \inst{1}%
  AUT Department
  \\IETR --- CentraleSupélec
  % \\[10pt]\\\includegraphics[width=1.5cm]{../img/logos/supelec.jpeg}
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

@@

\pgfdeclareimage[height=.8cm]{university-logo}{../img/logos/supelec.jpeg}
\logo{\pgfuseimage{university-logo}}

@@

    % The following outlook is optional.
    \vskip0pt plus.5fill
    \begin{itemize}
      \item
            Outlook
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
              \item
                    Non-linear attack model
            \end{itemize}
      \item Repository
\vspace{-.4cm}

                    \begin{minipage}{.6\textwidth}
                      \url{https://github.com/Accacio/SysTol-21}
                    \end{minipage}
                    \begin{minipage}{.2\textwidth}
                      \includegraphics[width=2cm]{../img/qrRepo.png}
                    \end{minipage}
    \end{itemize}
  \end{minipage}
\end{frame}
